---
title: SMARTS (Statistical Methods for Assessement of real-world Treatment Switching)
output: github_document
#bibliography: "references.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(knitr)
```

# SMARTS (Statistical Methods for Assessement of real-world Treatment Switching)

SMARTS is a tool to assign pseudo-switching time to patients who initiate a treatment and stay on the the treatment (continuers), in comparison to patients who initiate a treatment and switch to another treatment (switchers). The assigned pseudo-switching time is used in later analysis for reduce bias caused by time varying confounding.

## Install using devtools

```{r}
library(devtools)
install_github("chuangao/SMARTS")
```

## The package can also be rom source (see below) if this is the case.  

## Install from source

```bash
git clone https://github.com/chuangao/SMARTS
R CMD INSTALL SMARTS
```
## Example usage
```{r}
library(SMARTS)
data_tmp <- sim_data(n=500, seed=123,swi_min=1.5,swi_max=4.5, wshape_bf = 1, log_hr_confound = 2)
data <- list(cont = data_tmp %>% filter(swi == 0),
            swi = data_tmp %>% filter(swi == 1))
data_rand <- random_assign(data, nbin=10, seed=123, swi_time='xoyrs', cens_time = 'lot2_eventyrs_long')
```